Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-08 edubots_surveys.Rnw
Defined macro 'change' for changes
Deletes comments refs #50
Deletes comments refs #50 addresses first comment closes #53

\begin{keyword}
\kwd{Chatbots}
\kwd{Messaging platforms}
\kwd{Tutorship}
\kwd{Educational bots}
\kwd{Higher education}
% Antonio - add something related to "survey", "teachers' opinion" or so?
\end{keyword}

% MSC classifications codes, if any
%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                            %%
%% The Main Body begins here                  %%
%%                                            %%
%% Please refer to the instructions for       %%
%% authors on:                                %%
%% https://www.biomedcentral.com/getpublished %%
%% and include the section headings           %%
%% accordingly for your article type.         %%
%%                                            %%
%% See the Results and Discussion section     %%
%% for details on how to create sub-sections  %%
%%                                            %%
%% use \cite{...} to cite references          %%
%%  \cite{koon} and                           %%
%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
%%                                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The introduction of new technologies in the classroom involves a combination of
teacher training, student enthusiasm and possibly acquiring new skills by
both. Some technologies are readily adopted, but others require longer time for
full adoption. In most cases, the magnitude of the uptake of the new technology
impinges on the collaboration of all the parties using it. Hence, examining the
users’ opinions and is an important first step in boosting this collaboration
and reaping the benefits of the technology.  Recently, a surge in the use of
synchronous instant messaging tools in higher education such as WhatsApp,
Telegram and Facebook Messenger took place. Some messaging applications have
built-in chatbots to support a synchronous conversation between the different
parties \cite{differ.chat}, while other chatbots are developed as standalone
systems and can possibly be attached to a messaging application using an API
(Application Program Interface).

>>>>

\begin{keyword}
\kwd{Chatbots}
\kwd{Messaging platforms}
\kwd{Tutorship}
\kwd{Educational bots}
\kwd{Higher education}
\end{keyword}

@@

@@

The introduction of new technologies in the classroom, \textcolor{blue}{to be successful, involves extra
teacher training, devising methods for enhancing student engagement with the new
technology, and indeed acquiring new skills by students and teachers alike}.
Some technologies are readily adopted, but others require longer time for
full adoption. In most cases, the magnitude of the uptake of the new technology
impinges on the collaboration of all the parties using it. Hence, examining the
users’ opinions and is an important first step in boosting this collaboration
and reaping the benefits of the technology.  Recently, a surge in the use of
synchronous instant messaging tools in higher education such as WhatsApp,
Telegram and Facebook Messenger took place. Some messaging applications have
built-in chatbots to support a synchronous conversation between the different
parties \cite{differ.chat}, while other chatbots are developed as standalone
systems and can possibly be attached to a messaging application using an API
(Application Program Interface).
